---
title: "Final Draft"
author: 'Group Five '
date: "10/11/2016"
output: html_document
---

```{r Library, include=FALSE}
library(ggplot2)
library(reshape2)
library(grid)
library(scales)
library(sqldf)
library(rms)
library(pscl)
library(gridExtra)
library(dplyr)
library(stargazer)
library(xtable)
```

###Introduction(Marnelia):  
Who we are -> digital marketing consultant  
What we will do -> help our client, Tinder, keeps growing and find monetization opportunity

###Theory : what do you expect to find ? 
For our client , we want to use this dataset to solve 2 main problem?  

#### 1  What does dating app users look like?     
* Is there any characteristic of dating app users?  
* Can we use these characteristic to find our potential users?  
* Besides demographic data, this dataset also has behavioral data.   Can we use these data to improve our app?    
  
#### 2  How can Tinder grow? How can Tinder make money?      
* Where to advertise: social media, online shopping website....?  
* Other advertisement opportunity? We will use gaming and job data to see if these websites or apps can help us to recruit more users?  
* In return, after above strategy, when we have enough user base, we will consider to sell Ads in Tinder app. Can we consider these websites/apps as our potential advertisement buyers? If yes, what kind of data can support our argument?  


### Method:  
####1 Describe the dataset  
```{r}

cupid_data<-read.csv ("./Dataset/June 10-July 12, 2015 - Gaming, Jobs and Broadband - CSV.csv",colClasses="factor")
cupid_data[,"age"] <- as.numeric(cupid_data[,"age"])

# dimension (row*col)
# how many questions in each section
# how the dataset was collected (date and which research house)

```

### Data Cleansing ###

ASK ALL:
EMPLNW	Are you now employed full-time, part-time, retired, or are you not employed for pay? {PIAL trend – added 98 ‘DK’ and change REF from ‘9’ to ‘99’}
1	Employed full-time
2	Employed part-time
3	Retired
4	Not employed for pay
5	(VOL.) Have own business/self-employed
6	(VOL.) Disabled
7	(VOL.) Student
8	(VOL.) Other
98	(VOL.) Don't know
99	(VOL.) Refused
```{r}
table(cupid_data$emplnw)
# The following factors (1,2,3,4) represent 1896/2001 respondents. They are retained while factors (5,6,7,8,98,99) will be recategorised as others. a

cupid_data$emplnw_group <-""
for (i in 1:(nrow(cupid_data))){
  if(cupid_data[i,"emplnw"] == "1") cupid_data[i,"emplnw_group"] <- "Employed"
  if(cupid_data[i,"emplnw"] == "2") cupid_data[i,"emplnw_group"] <- "Employed"
  if(cupid_data[i,"emplnw"] == "3") cupid_data[i,"emplnw_group"] <- "Retired"
  if(cupid_data[i,"emplnw"] == "4") cupid_data[i,"emplnw_group"] <- "Not employed"
  if(cupid_data[i,"emplnw"] == "5") cupid_data[i,"emplnw_group"] <- "Not employed" 
  if(cupid_data[i,"emplnw"] == "6") cupid_data[i,"emplnw_group"] <- "Not employed"
  if(cupid_data[i,"emplnw"] == "7") cupid_data[i,"emplnw_group"] <- "Not employed"
  if(cupid_data[i,"emplnw"] == "8") cupid_data[i,"emplnw_group"] <- "Not employed"
  if(cupid_data[i,"emplnw"] == "98") cupid_data[i,"emplnw_group"] <- "Others"
  if(cupid_data[i,"emplnw"] == "99") cupid_data[i,"emplnw_group"] <- "Others"
  }
cupid_data$emplnw_group <- factor(cupid_data$emplnw_group)
table(cupid_data$emplnw_group)
```

ASK IF EMPLOYED (EMPLNW=1,2,5):
EMPTYPE1	How would you describe the place where you work? [READ]
1	A large corporation
2	A medium-size company
3	A small business
4	A part of the federal, state or local government
5	A school or educational institution, OR
6	A non-profit organization?
7	(VOL.) Other
8	(VOL.) Self-employed/work at home
98	(VOL.) Don’t know
99	(VOL.) Refused
```{r}
table(cupid_data$emptype1)
# The following factors (1,2,3,4,5) represent 963/1100 respondents for the question. Factor 4 & 5 will be re-categorised as Public Sector. The factors (6,7,8,98) will be recategorised as others. 

cupid_data$emptype1_group <-""

for (i in 1:(nrow(cupid_data))){
  ifelse(cupid_data[i,"emptype1"] == 1, cupid_data[i, "emptype1_group"] <- "A large corporation",
  ifelse(cupid_data[i,"emptype1"] == 2, cupid_data[i,"emptype1_group"] <- "A medium-size company", 
  ifelse(cupid_data[i,"emptype1"] == 3, cupid_data[i,"emptype1_group"] <- "A small business", 
  ifelse(cupid_data[i,"emptype1"] == 4, cupid_data[i,"emptype1_group"] <- "Public Sector", 
  ifelse(cupid_data[i,"emptype1"] == 5, cupid_data[i,"emptype1_group"] <- "Public Sector",
  ifelse(cupid_data[i,"emptype1"] == 6, cupid_data[i,"emptype1_group"] <- "Others",
  ifelse(cupid_data[i,"emptype1"] == 7, cupid_data[i,"emptype1_group"] <- "Others",
  ifelse(cupid_data[i,"emptype1"] == 8, cupid_data[i,"emptype1_group"] <- "Others",
  ifelse(cupid_data[i,"emptype1"] == 98, cupid_data[i,"emptype1_group"] <- "Others",
  ifelse(cupid_data[i,"emptype1"] == 99, cupid_data[i,"emptype1_group"] <- "Others",
  cupid_data[i,"emptype1_group"] <- "No data"))))))))))
  }
cupid_data$emptype1_group <- factor(cupid_data$emptype1_group)
table(cupid_data$emptype1_group)

```

ASK ALL:
INC	Last year -- that is in 2014 -- what was your total family income from all sources, before taxes? Just stop me when I get to the right category... [READ] {Master INC2}
1	Less than $10,000
2	10 to under $20,000
3	20 to under $30,000
4	30 to under $40,000
5	40 to under $50,000
6	50 to under $75,000
7	75 to under $100,000
8	100 to under $150,000
9	$150,000 or more
98	(VOL.) Don't know
99	(VOL.) Refused


```{r}
table(cupid_data$inc)
# The team created 4 categories of income level for this analysis.For a sample size of 2001, there are 1696 who revealed their salary. The income is then segregated into 4 main groups as follows.
# Bottom one-third(524 pax) - Between 0 - 30000
# Middle one-third(604) - Between 30000 - 75000
# Upper one-third(405) - Between 75000 - 150000
# Ultra-rich(163) - Above 150000
# Refused/Don't Know(305) 

cupid_data$inc_group <-""
  
for (i in 1:(nrow(cupid_data))){
  if(cupid_data[i,"inc"] == "1") cupid_data[i,"inc_group"] <- "Low-income" 
  if(cupid_data[i,"inc"] == "2") cupid_data[i,"inc_group"] <- "Low-income"
  if(cupid_data[i,"inc"] == "3") cupid_data[i,"inc_group"] <- "Low-income"
  if(cupid_data[i,"inc"] == "4") cupid_data[i,"inc_group"] <- "Middle-income"
  if(cupid_data[i,"inc"] == "5") cupid_data[i,"inc_group"] <- "Middle-income"
  if(cupid_data[i,"inc"] == "6") cupid_data[i,"inc_group"] <- "Middle-income"
  if(cupid_data[i,"inc"] == "7") cupid_data[i,"inc_group"] <- "Upper-income"
  if(cupid_data[i,"inc"] == "8") cupid_data[i,"inc_group"] <- "Upper-income"
  if(cupid_data[i,"inc"] == "9") cupid_data[i,"inc_group"] <- "Upper-income"
  if(cupid_data[i,"inc"] == "98") cupid_data[i,"inc_group"] <- "Others"
  if(cupid_data[i,"inc"] == "99") cupid_data[i,"inc_group"] <- "Others"  
}
cupid_data$inc_group <-factor(cupid_data$inc_group)
table(cupid_data$inc_group)

```


RACE	What is your race? Are you white, black, Asian, or some other race?
IF R SAYS HISPANIC OR LATINO, PROBE: Do you consider yourself a WHITE (Hispanic/Latino) or a BLACK (Hispanic/Latino)? IF R DOES NOT SAY WHITE, BLACK OR ONE OF THE RACE CATEGORIES LISTED, RECORD AS “OTHER” (CODE 6)
1	White
2	Black or African-American
3	Asian or Pacific Islander
4	Mixed race
5	Native American/American Indian
6	Other (SPECIFY)
8	(VOL.) Don't know
9	(VOL.) Refused

```{r}

table(cupid_data$race)
# Factors (1, 2, 3) represent 1813/2001 of the respondents. Hence factors (1, 2, 3) are retained while the remaining factors are recategorised.
cupid_data$race_group <-""
  
for (i in 1:(nrow(cupid_data))){
  if(cupid_data[i,"race"] == "1") cupid_data[i,"race_group"] <- "White" 
  if(cupid_data[i,"race"] == "2") cupid_data[i,"race_group"] <- "Black"
  if(cupid_data[i,"race"] == "3") cupid_data[i,"race_group"] <- "Asian"
  if(cupid_data[i,"race"] == "4") cupid_data[i,"race_group"] <- "Others"
  if(cupid_data[i,"race"] == "5") cupid_data[i,"race_group"] <- "Others"
  if(cupid_data[i,"race"] == "6") cupid_data[i,"race_group"] <- "Others"
  if(cupid_data[i,"race"] == "8") cupid_data[i,"race_group"] <- "Unknown/Rejected"
  if(cupid_data[i,"race"] == "9") cupid_data[i,"race_group"] <- "Unknown/Rejected"
}

table(cupid_data$race_group)

```

```{r}
#regroup marriage status
table(cupid_data$marital_group)
cupid_data$marital_group <-""
for (i in 1:(nrow(cupid_data))){
  if(cupid_data[i,"marital"] == 1) cupid_data[i,"marital_group"] <- "Married or have a partner" 
  if(cupid_data[i,"marital"] == 2) cupid_data[i,"marital_group"] <- "Married or have a partner"
  if(cupid_data[i,"marital"] == 3) cupid_data[i,"marital_group"] <- "Not married"
  if(cupid_data[i,"marital"] == 4) cupid_data[i,"marital_group"] <- "Not married"
  if(cupid_data[i,"marital"] == 5) cupid_data[i,"marital_group"] <- "Not married"
  if(cupid_data[i,"marital"] == 6) cupid_data[i,"marital_group"] <- "Not married"
  if(cupid_data[i,"marital"] == 8) cupid_data[i,"marital_group"] <- "Others"
  if(cupid_data[i,"marital"] == 9) cupid_data[i,"marital_group"] <- "Others"
}
cupid_data$marital_group <-factor(cupid_data$marital_group)
table(cupid_data$marital_group)

#regroup ideology
table(cupid_data$ideo)
cupid_data$ideo_group <-""

for (i in 1:(nrow(cupid_data))){
  if(cupid_data[i,"ideo"] == 1) cupid_data[i,"ideo_group"] <- "Conservative" 
  if(cupid_data[i,"ideo"] == 2) cupid_data[i,"ideo_group"] <- "Conservative"
  if(cupid_data[i,"ideo"] == 3) cupid_data[i,"ideo_group"] <- "Moderate"
  if(cupid_data[i,"ideo"] == 4) cupid_data[i,"ideo_group"] <- "Liberal"
  if(cupid_data[i,"ideo"] == 5) cupid_data[i,"ideo_group"] <- "Liberal"
  if(cupid_data[i,"ideo"] == 8) cupid_data[i,"ideo_group"] <- "Others"
  if(cupid_data[i,"ideo"] == 9) cupid_data[i,"ideo_group"] <- "Others"
}
cupid_data$ideo_group <-factor(cupid_data$ideo_group)
table(cupid_data$ideo_group)

#regroup education status
table(cupid_data$educ2)
cupid_data$educ2_group <-""

for (i in 1:(nrow(cupid_data))){
  if(cupid_data[i,"educ2"] == 1) cupid_data[i,"educ2_group"] <- "less than university degree" 
  if(cupid_data[i,"educ2"] == 2) cupid_data[i,"educ2_group"] <- "less than university degree"
  if(cupid_data[i,"educ2"] == 3) cupid_data[i,"educ2_group"] <- "less than university degree"
  if(cupid_data[i,"educ2"] == 4) cupid_data[i,"educ2_group"] <- "university with/without degree"
  if(cupid_data[i,"educ2"] == 5) cupid_data[i,"educ2_group"] <- "university with/without degree"
  if(cupid_data[i,"educ2"] == 6) cupid_data[i,"educ2_group"] <- "university with/without degree"
  if(cupid_data[i,"educ2"] == 7) cupid_data[i,"educ2_group"] <- "postgraduate degree or more"
  if(cupid_data[i,"educ2"] == 8) cupid_data[i,"educ2_group"] <- "postgraduate degree or more"
  if(cupid_data[i,"educ2"] == 98) cupid_data[i,"educ2_group"] <- "Others"
  if(cupid_data[i,"educ2"] == 99) cupid_data[i,"educ2_group"] <- "Others"

}
cupid_data$educ2_group <-factor(cupid_data$educ2_group)
table(cupid_data$educ2_group)
```


####2 Strength  
####3 Limitation  
(Laurence, can you kindly help to fill first part?)
```{r}
# 1. Proportion of ethnicity within sample is not representative of the real population
us_race <- c("White", "Black", "Asian", "Others")
us_race_perc <- c(72.4, 12.6, 4.8, 10.2)
us_race_df <- data.frame(us_race, us_race_perc)
us_race_plot <- ggplot(data = us_race_df) + geom_bar(aes(x="Race Composition", y=us_race_perc, fill = us_race), stat ="identity") + ylab("% Composition")

survey_race_df<-data.frame(table(cupid_data$race_group))
names(survey_race_df)<- c ("survey_race", "survey_race_perc")

survey_race_plot <- ggplot(data = survey_race_df[c(1:3,5),]) + geom_bar(aes(x="Race Composition", y=survey_race_perc/1974*100, fill = survey_race), stat ="identity") + ylab("% Composition")

grid.arrange(survey_race_plot, us_race_plot, ncol =2)
# 2. Age group within sample is not representative of the real population. Approximately 50% of the respondents are between the age 50-75.

ggplot(data = cupid_data) + geom_density(aes(x = age))

```


### Analysis  

### 1. What does dating app users look like?

#### 1.1 How does our original user look like? demographic analysis (Lawrence & Marnelia) (Yerik)
Income, employment - Lawrence
```{r}
## your code here
```

Age,gender,ideology,..... - Marnelia
```{r}
## your code here
```

Other interesting - Yerik
```{r}
## your code here
```


Insight : summarize a few demographic traits of our original users

#### 1.2 How does our potential users look like? demographic analysis (Marnelia)   
Marnelia will use opinion about online dating to group users (eg. anyone who agree with more than three dating opinion will be grouped into potential users.)

```{r}
## your code here
## Find our target users (potential users who are not against online dating but haven't use it before)
```

Insight :summarize a few demographic traits of our potential



### 2. How to grow and make money?
#### 2.1 The most tradition way of growing is through paid media and collaboration. Can we know more about our users digital profile, such as online shopping, social media, and use this insight to form our marketing strategy? (Mei)

## Social Media
This part is to analyse whether people who used social media sites such as Facebook, Twitter or LinkedIn to look for a job, to apply for a job that you found out about on social media or to let their friends know about a job, tend to use online dating app or website.

```{r,echo=FALSE}

## your code here
## the relationship between people's preference or habits of cellphone and Internet in daily life and online dating preference
## According to the characteristic of potential users, make our marketing strategy ( where to advertise: social media, online shopping website...) 

# 1 : Social media 

# question (snsjob1):
# Thinking about social media sites like Facebook, Twitter or LinkedIn… Have you ever
# snsjob1a.	Used social media to look for or research a job
# snsjob1b.	Applied for a job that you found out about on social media
# snsjob1c.	Used social media to let your friends know about a job that was available at your place of employment

# data preparation

tab <- cupid_data[,c("date1a","date2a", "snsjob1a", "snsjob1b", "snsjob1c")]
tab <- filter(tab, date1a == 1|date1a == 2,date2a == 1|date2a == 2,
                      snsjob1a == 1|snsjob1a == 2, 
                      snsjob1b == 1|snsjob1b == 2, 
                      snsjob1c == 1|snsjob1c == 2)
# if social media preference = 1, it means he use social media to do job searching related activity; if it is 0, means never use it to do such kind of activity.
tab[,"social_media_pref"] <- 1
for (i in 1:nrow(tab)){
  if (tab[i, "snsjob1a"] == 2 & tab[i, "snsjob1b"] == 2 & tab[i, "snsjob1c"] == 2) {
    tab[i, "social_media_pref"] <- 2
  }
}
tab[,"dating"] <- 1
for (i in 1:nrow(tab)){
  if (tab[i, "date1a"] == 2 &  tab[i, "date2a"] == 2) {
    tab[i, "dating"] <- 2
  }
}
tab$social_media_pref <- factor(tab$social_media_pref)
tab$dating <- factor(tab$dating)

#chi square test and fequency table
pvalue <- chisq.test(table(tab$dating, tab$social_media_pref))$p.value

social.table <- xtable(table(factor(tab$dating,labels=c("Yes","No")),factor(tab$social_media_pref,labels=c("Used","Not used"))))

#logistic model
model.social <- glm(dating ~ social_media_pref, data = tab, family = "binomial")
summary(model.social)
pr2 <- pR2(model.social)

```
P value is $pvalue$ less than 0.05 and the coefficient of logistic model is significant. so the there is a relationship between using online dating app and using social media to find a job.

## cellphone preference and online dating app

```{r}

# 2. cellphone preference and online dating app
# question (q5)  Do you ever use your cell phone to
# q5a.	Participate in a video call or video chat {modified Master CELLVCHT}
# q5b.	Buy a product online, such as books, music, toys or clothing {New}
# q5c.	Get directions, recommendations, or other information related to your location

cellphone.tab <- cupid_data[ ,c("date2a", "q5a", "q5b", "q5c")]
cellphone.tab <- filter(cellphone.tab, 
                        date2a == 1|date2a == 2,
                        q5a == 1|q5a == 2,
                        q5b == 1|q5b == 2,
                        q5c == 1|q5c == 2 )

p.val2 = matrix(nrow = ncol(cellphone.tab), ncol = ncol(cellphone.tab))
for (i in 1:ncol(cellphone.tab)){
  for (j in 1:ncol(cellphone.tab)){
    tab2 <- data.frame(cellphone.tab[ ,i],cellphone.tab[ ,j])
    table.test <- table(tab2)
    p.val2[i, j] <- chisq.test(table.test)$p.value
  }
}

model.cellphone <- glm(factor(date2a) ~ factor(q5a), 
                       data = cellphone.tab, 
                       family = "binomial")
summary(model.cellphone)
pR2(model.cellphone)
fitod <- glm(factor(date2a) ~ factor(q5a),
             data = cellphone.table,
             family = "quasibinomial")
pchisq(summary(fitod)$dispersion * model.cellphone$df.residual, 
       model.cellphone$df.residual, lower=F)

model.cellphone <- glm(factor(date2a) ~ factor(q5b), 
                       data = cellphone.tab, 
                       family = "binomial")
summary(model.cellphone)
pR2(model.cellphone)
#test whether there is an overdispersion
fitod <- glm(factor(date2a) ~ factor(q5b),
             family = "quasibinomial")
pchisq(summary(fitod)$dispersion * model.cellphone$df.residual, 
       model.cellphone$df.residual, lower=F)




```

```{r}
# 3.Influece of Demographic Data, job searching and cellphone preference on whether to use online dating app
job.table <- cupid_data[ ,c("date1a","date2a", "q5a", "q5b", "snsjob1a", "snsjob1b", "snsjob1c", "age", "sex", "educ2_group", "marital_group", "party", "inc_group", "race", "emplnw_group", "ideo_group")]

job.table <- filter(job.table, 
                    date1a == 1|date1a == 2,
                    date2a == 1|date2a == 2,
                    q5a == 1|q5a == 2, q5b == 1|q5b == 2,
                    snsjob1a == 1|snsjob1a == 2,snsjob1b == 1|snsjob1b == 2, 
                    snsjob1c == 1|snsjob1c == 2,
                    age < 97, inc_group != "Others", marital_group != "Others",
                    educ2_group != "Others", party != 8, party != 9,
                    race != 9, race != 8, emplnw_group != "Others", ideo_group != "Others")

# if social media preference = 1, it means he use social media to do job searching related activity; if it is 0, means never use it to do such kind of activity.
job.table[,"social_media_pref"] <- 1
for (i in 1:nrow(job.table)){
  if (job.table[i,"snsjob1a"] == 2 & job.table[i,"snsjob1b"] == 2 & job.table[i,"snsjob1c"] == 2) {
    job.table[i, "social_media_pref"] <- 2
  }
}
job.table[,"social_media_pref"] <- factor(job.table[,"social_media_pref"] )
job.table[,"dating"] <- 1
for (i in 1:nrow(job.table)){
  if (job.table[i,"date1a"] == 2 & job.table[i,"date2a"] == 2 ) {
    job.table[i, "dating"] <- 2
  }
}
job.table[,"dating"] <- factor(job.table[,"dating"])

chisq.test(job.table$q5a,job.table$social_media_pref)

model.logit <- glm(dating ~ q5a + q5b + social_media_pref
                    + age + sex + educ2_group + marital_group + party + inc_group + race + emplnw_group + ideo_group, data = job.table, family = "binomial")
summary(model.logit)
pR2(model.logit)

model.logit2 <- glm(factor(date2a) ~factor(social_media_pref) + age + factor(marital), 
                    data = job.table, 
                    family = "binomial")
summary(model.logit2)
pR2(model.logit2)

model.logit2 <- glm(factor(date2a) ~factor(q5b) + age + factor(marital), 
                    data = job.table, 
                    family = "binomial")
summary(model.logit2)
pR2(model.logit2)

#test whether there is overdispersion
fitod <- glm(factor(date2a) ~ factor(q5b) + age + factor(marital), 
             data = job.table, 
             family = "quasibinomial")
pchisq(summary(fitod)$dispersion * model.logit2$df.residual, model.logit2$df.residual, lower=F)

```

Insight : summarize a few behavior traits of our users and potential users

#### 2.2 Other advertisement opportunity? We will use gaming and job data to see if these websites or apps can help us to recruit more users?  (Chewei and Mei-job, Vrat and Yerik-gaming )
```{r CHEWEI AND MEI}
## your code here -chewei and mei
## relationship between job searching preference and online dating preference  (Mei & Zhewei)
```

Insight: Can we use gaming/job website as one of growth channel?
######Sample distribution of gaming response across gender and age group
```{r, echo = FALSE,out.width = "60%", fig.align = "center"}
#Yerik
game1 <- cupid_data[cupid_data["game1"] == c(1,2),]
#summary(game1)

#Gender
p1 <- ggplot(data = game1)+geom_bar(aes(x=factor(game1,levels=c(1,2),labels=c("Yes","No")),fill=factor(sex)),position="dodge",stat="count")+labs(x="", y="No. of Respondents", title="Have you ever played video games?-Gender")

#Age
for (i in 1:nrow(game1)) {
  if (game1[i,"age"]<= 35) game1[i,"ageGroup"] <- "<=35"
  if (game1[i,"age"] > 35 & game1[i,"age"] <= 50) game1[i,"ageGroup"] <- "<=50"
  if (game1[i,"age"] > 50 & game1[i,"age"] <= 65) game1[i,"ageGroup"] <- "<=65"
  if (game1[i,"age"] > 65) game1[i,"ageGroup"] <- ">65"
}
p2 <- ggplot(data = game1)+geom_bar(aes(x=factor(game1,levels=c(1,2),labels=c("Yes","No")),fill=ageGroup),position="dodge",stat="count")+labs(x="", y="No. of Respondents", title="Have you ever played video games?-Age")
grid.arrange(p1,p2)
```
 
######Whether there is a difference in age and gender in terms of gaming in the population? 

Chi-squared test is used to test whether there is an inequal distribution in gaming population across gender and age group.

H0: There is no gender difference in the distribution of playing or not playing game in population
```{r, echo = FALSE,out.width = "60%", fig.align = "center"}
#Yerik
#Proportion test (H0: There is no gender difference in the distribution of playing or not playing game in population)
game1_test <- game1[game1[,"game1"]==c(1,2),c("sex","game1")]
#summary(game1_test)
chisq.test(table(game1_test))
```
p-value is 0.935, which fails to reject H0.

H0: There is no age difference in the distribution of playing or not playing game in population
```{r, echo = FALSE,out.width = "60%", fig.align = "center"}
#There is no gender difference among gaming people
#No need to analyse game3
game1_test <- game1[game1[,"game1"]==c(1,2),c("ageGroup","game1")]
#summary(game1_test)
chisq.test(table(game1_test))
#There is age difference among gaming people
```
p-value is 2.954e-09, which rejects H0 at 1% of significance level.

From above two tests, we conclude  that there is a significant inequal distribution across age group in gaming population.

######Relationship between gaming and online dating
```{r, echo = FALSE,out.width = "60%", fig.align = "center"}
#Yerik
#game1=1,date
date1a.game1 <- game1[game1["date1a"]==c(1,2),c("date1a","game1")]
date1a.game1 <- na.omit(date1a.game1)
date2a.game1 <- game1[game1["date2a"]==c(1,2),c("date2a","game1")]
date2a.game1 <- na.omit(date2a.game1)
#summary(date2a.game1)
p1 <- ggplot(data=date1a.game1)+geom_bar(aes(x=factor(date1a),fill=factor(game1)),position="dodge",stat="count")+labs(x="Dating Sites Usage", y="No. of Respondents", title="The Relationship between Gaming and Dating Sites Usage")
p2 <- ggplot(data=date2a.game1)+geom_bar(aes(x=factor(date2a),fill=factor(game1)),position="dodge",stat="count")+labs(x="Dating App Usage", y="No. of Respondents", title="The Relationship between Gaming and Dating App Usage")
grid.arrange(p1,p2)
```

The two charts indicate that among either group who did or did not have online dating experience, more than 50% percent played game before. (how to deduce that this conclusion applies in population?)

```{r, echo = FALSE,out.width = "60%", fig.align = "center"}
#chisq.test (is it appropraite to use chisq.test here?)
chisq.test(table(date1a.game1))
chisq.test(table(date2a.game1))
```

#### 2.3 After the phase of growth, we will seek monetization opportunity. Are the mentioned websites and app our potential advertisement buyers? (Chewei and Mei-job, Vrat and Yerik-gaming )
#####2.3.1 Difference of online dating between employment status.
###### Assumption: In this question, we are going to lay the foundatino for our monetization strategy. This part will analyze  our users' employment status and if our users are attractive customers of advertisers. 
*In this quesiton, we foucs more on people who use dating app. 

```{r CHEWEI2, echo=FALSE, include=FALSE}
## your code here -chewei and mei
## relationship between job searching preference and online dating preference  (Zhewei)
cupid_data1 <- read.csv ( "./Dataset/June 10-July 12, 2015 - Gaming, Jobs and Broadband - CSV.csv", colClasses = "factor" )
cupid_data1 <- tbl_df( cupid_data1 )
cupid_data1<-cbind(cupid_data1,cupid_data$emplnw_group,             cupid_data$inc_group, cupid_data$educ2)
#cupid_data1$`cupid_data$emplnw_group`
datingpeople <- cupid_data1 %>% filter (( eminuse == 1 | intmob                   ==1 ) & smart1 == 1 )
```


```{r}
ggplot(data=cupid_data1,aes(x=`cupid_data$emplnw_group`))+geom_bar(aes(fill=sex))
datejobtable<-table(  
              cupid_data1$`cupid_data$emplnw_group`,cupid_data1$date2a)
# exclude emplnw 5~9 (since too little obeservation, and date2a)
datejobtable<-datejobtable[,2:3] 
datejobtable
chisq.test(datejobtable)
```
From above graphic, we can find that people who have full-time work are more likely to be a dating app users. We futher conduct a chi-square test to testify if dating app usage will affect their employment status. The p-value is 0.07, quite close to 0.05 siginificant level. Therefore, we prove that our users are potential customers for advertiser.   
##### Action : We will use this figure in our sales kit to convince our advertisers that by investing in our in-app AD, they can acquire huge return. 

#### 2.3.2: Is there a model can be used to describe job emplyment and dating app usage?  
#### Assumption: We narrow down our potential customers to online job websites. Here we are going to access if there is any model we can use to predict one's usage of online job seeking.
```{r}
datingpeople[,"age"]<-as.numeric(unlist(datingpeople[,"age"]))
for (i in 1:nrow(datingpeople)){
  if (datingpeople[i,"marital"]=="1"){
    datingpeople[i,"clsmari"]=1
  }
  else if (datingpeople[i,"marital"]=="2"){
    datingpeople[i,"clsmari"]=1
  }
  else{
    datingpeople[i,"clsmari"]=2
  }
}

ggplot(datingpeople, aes(x=smjob1))+geom_bar(aes(fill=date2a))
dating_between<-glm(smjob1~date2a+age+clsmari,data=datingpeople,family = "binomial")
summary(dating_between)
pR2(dating_between)
#exp(confint(dating_between))
#require(rms)
#mm<-lrm(smjob1~date2a,data=datingpeople)
#summary(mm)
```
If we use date2a (usin dating app) as predictaor of smjob1(using mobile phone to find job), the p-value of intercept, which is the base case of using dating app, is less than 0.05 significance; and p-value of date2a, which is not using dating app, is less than 00.05 significance. 
#### Action: Merely using dating and age can give us 12% of R^2. We believe that if we can combine more demographic targeting in our tinder database, then we can have a more accurate targeting system for our advertisers. 


```{r, echo = FALSE,out.width = "60%", fig.align = "center"}
## your code here Yerik
date1a <- cupid_data[cupid_data["date1a"] == c(1,2),c("date1a","age")]
date1a <- na.omit(date1a)
for (i in 1:nrow(date1a)) {
  if (date1a[i,"age"]<= 35) date1a[i,"ageGroup"] <- "<=35"
  if (date1a[i,"age"] > 35 & date1a[i,"age"] <= 50) date1a[i,"ageGroup"] <- "<=50"
  if (date1a[i,"age"] > 50 & date1a[i,"age"] <= 65) date1a[i,"ageGroup"] <- "<=65"
  if (date1a[i,"age"] > 65) date1a[i,"ageGroup"] <- ">65"
}
p1 <- ggplot(data=date1a)+geom_bar(aes(x=factor(date1a),fill=ageGroup),position="dodge",stat="count")+labs(x="Online Dating Sites Usage", y="No. of Respondents", title="Online Dating Sites Usage across Age Group")

date2a <- cupid_data[cupid_data["date2a"] == c(1,2),c("date2a","age")]
date2a <- na.omit(date2a)
for (i in 1:nrow(date2a)) {
  if (date2a[i,"age"]<= 35) date2a[i,"ageGroup"] <- "<=35"
  if (date2a[i,"age"] > 35 & date2a[i,"age"] <= 50) date2a[i,"ageGroup"] <- "<=50"
  if (date2a[i,"age"] > 50 & date2a[i,"age"] <= 65) date2a[i,"ageGroup"] <- "<=65"
  if (date2a[i,"age"] > 65) date2a[i,"ageGroup"] <- ">65"
}
p2 <- ggplot(data=date2a)+geom_bar(aes(x=factor(date2a),fill=ageGroup),position="dodge",stat="count")+labs(x="Online Dating App Usage", y="No. of Respondents", title="Online Dating App Usage across Age Group")
grid.arrange(p1,p2)
```

From the charts, we can see the online dating usage across different age groups. Those under 50 are more likely to become online dating users. So, will the factor of "gaming" help transform those potential users into users?

```{r, echo = FALSE,out.width = "60%", fig.align = "center"}
date1a.game1 <- game1[game1["date1a"]==2,c("game1","ageGroup")]
date1a.game1 <- na.omit(date1a.game1)
p1 <- ggplot(data=date1a.game1)+geom_bar(aes(x=ageGroup,fill=factor(game1)),position="dodge",stat="count")+labs(x="Age Group", y="No. of Respondents", title="Gaming across Age Group for Potential Users (no for online dating sites)")

date2a.game1 <- game1[game1["date2a"]==2,c("game1","ageGroup")]
date2a.game1 <- na.omit(date2a.game1)
p2 <- ggplot(data=date2a.game1)+geom_bar(aes(x=ageGroup,fill=factor(game1)),position="dodge",stat="count")+labs(x="Age Group", y="No. of Respondents", title="Gaming across Age Group for Potential Users (no for online dating app)")
grid.arrange(p1,p2)
```

For our potential users (people who answered "no" for online dating experience), a large portion played game, espeically for age group under 50. Doing advertisement on video games would be an effective strategy to attract more users for Tinder.

Insight: Can we sell ads to these websites/apps?

### Conclusion

#### 1 . Summarize what we find interesting
#### 2 . Next step : What do we suggest Tinder to do?
#### 3 . Further study : What kind of data we want to include in this dataset?
